Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-02-27 paper.tex
comments and addition to section IV

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints.
	\item handling of concurrent software.
	\item platform restrictions.
	\item legacy designs. %, which are usually developed with low-level languages.
	\item support to different programming languages and interfaces.
	\item handling of non-linear and non-convex optimization problems.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The fifth aspect is related to the evolution of development processes and technologies, which may delay the application of suitable verification and synthesis approaches if verifiers and synthesizers do not support different programming languages and interfaces. Finally, the last one is related to the widespread use of embedded systems in autonomous vehicles navigation systems~\cite{Adouane16}, which demand optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic.

Those five challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where the controlled object ({\it e.g.}, physical plant) typically exhibits continuous behavior whereas the controller (usually implemented by a real-time computer system) operates in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of the quantizers (A/D and D/A converters) when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered when correct-by-construction code is generated for embedded systems.

@@

Section~\ref{achievements} outlines contributions toward these research problems.

>>>>

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. \textcolor{red}{nao faltou completeness? talvez fosse bom colocar algumas palavras disso, o que fecharia com BMC e k-induction} Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints.
	\item handling of concurrent software.
	\item platform restrictions.
	\item verification of code pieces or modules that rely on larger structures.
	\item legacy designs. %, which are usually developed with low-level languages.
	\item support to different programming languages, frameworks, and interfaces.
	\item Correct code instrumentation \textcolor{red}{vale a pena mencionar que precisamos instrumentar corretamente o codigo?}.
	\item handling of non-linear and non-convex optimization problems.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect deals with code that uses an existing infrastructure and must be compliant with that, such as Linux kernel modules. The fifth aspect, in turn, is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The sixth aspect is related to the evolution of development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. Finally, the last one is related to the widespread use of embedded systems in autonomous vehicles navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic.

Those seven challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where the controlled object ({\it e.g.}, physical plant) typically exhibits continuous behavior whereas the controller (usually implemented by a real-time computer system) operates in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of the quantizers (A/D and D/A converters) when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered when correct-by-construction code is generated for embedded systems.

@@

\textcolor{red}{serah demais mencionar um framework unificado, que abranja tanto propriedades de bauxo nivel e comportamento quanto descricoes de alto nivel?}
Section~\ref{achievements} outlines contributions toward these research problems.
